The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-11 paper/ms.tex
minor changes

\begin{figure*}
    \includegraphics[width=1.0\textwidth]{f2.eps}
    \caption{Half-width for the non-dusty models as a function of
      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
      correspond to central (homogeneous) source
      distributions. \label{fig:widthvsvelocity}} 
\end{figure*}

\begin{figure}
    \includegraphics[scale=0.4]{f3.eps}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

We use the full width at half maximum (FWHM), $W$, to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
with rotational velocity. {\bf Here we need to check the numbers to
  say something more specific.}

We parameterize the dependency of the linewidth as $W^2 =
W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity width can be expressed as a
quadratic sum of the two relevant velocities in the problem. By
fitting simultaneously all the data points corresponding to central
and homogeneous models we find $\lambda_{\rm c} = 3.9 \pm$ and
$\lambda_{\rm h}= 1.9\pm $ respectively.

@@

\begin{figure}
    \includegraphics[scale=0.4]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.4]{f6.eps}
  \caption{Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models.
    \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.4]{f7.eps}
  \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
    \label{fig:efvsNeufeld}}   
\end{figure}

@@

\label{sec:off-center}
\begin{figure}
\begin{center}
  \includegraphics[scale=0.4]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. 
    \label{fig:OCspheres}}

@@

\begin{figure}
  \includegraphics[scale=0.4]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

@@

\begin{figure*}
\includegraphics[scale=0.4]{f11.eps}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.9\textwidth]{f2.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of
    rotational velocity $V_{\rm max}$. The left panel shows the
    results in velocity units while the right panel normalizes
    the data by the FWHM in the static case. 
    Continuous (dashed) lines  correspond to central (homogeneous)
    source distributions. The straight lines represent the fit to
    the data using the expresion in Eq. (\ref{eq:fwhm}).
    \label{fig:widthvsvelocity}} 
\end{figure*}

\begin{figure}
    \includegraphics[scale=0.35]{f3.eps}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure}

@@

We use the full width at half maximum (FWHM) to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $FWHM$ increases
with rotational velocity both for the central an homogeneous source
distributions.  We parameterize the dependency of the linewidth as
\begin{equation}
 FWHM^2 = FWHM_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where $FWHM_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.9 \pm$ and $\lambda_{\rm h}=
1.9\pm $ respectively.

@@

\begin{figure}
    \includegraphics[scale=0.35]{f4.eps}
\caption{Logarithm of the average number of scatterings as function of
  rotational velocity. Continuous (dashed) lines represent an
  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.35]{f6.eps}
  \caption{Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models.
    \label{fig:efvsv}}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.35]{f7.eps}
  \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
    \label{fig:efvsNeufeld}}   
\end{figure}

@@

\label{sec:off-center}
\begin{figure}
\begin{center}
  \includegraphics[scale=0.35]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. 
    \label{fig:OCspheres}}

@@

\begin{figure}
  \includegraphics[scale=0.35]{f9.eps}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.35]{f11.eps}
\end{center}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}
